{\bf \Large TO BE RENAMED}

### 2023-05-23 draft.tex
no commit message

\title{{\bf \Large THESISSSS}
}

@@

Conceptualizations of contextual effects commonly hinge on the choice frequency comparisons between two alternatives. For example, in case of attraction effect, if adding a third alternative to a two-item menu induces some of the consumers to switch their choices to the other incumbent alternative – one could conclude that attraction effect is present. This is suitable for experimental setups where researcher has control over menus and can observe choices in both cases (i.e., in case of an original two-item menu, as well as after adding the third item). However, given that the aim is to generalize context effect measures for application to a wider range of situations, and most importantly to observational data, it is necessary to take a more fine-grained view and quantify the context in which each of the alternatives is embedded. Quantifying the choice context for each alternative would create opportunity to study the effect of the context on choice probabilities through inference across (very) different choice sets. Such an approach would be general enough to consider not only addition of a new alternative to the menu, but also any alteration of attributes for any of the items in the menu. For example, increasing price of an alternative could decrease the probability of its choice. This would have a direct effect on choice probabilities of other alternatives. However, the same price increase could also change the choice context and have additional knock-on effect on choice probabilities of (at least some) alternatives.

>>>>

\title{{\bf \Large TO BE RENAMED}
}

@@

Conceptualizations of contextual effects commonly hinge on the choice frequency comparisons between two alternatives. For example, in case of attraction effect, if adding a third alternative to a two-item menu induces some of the consumers to switch their choices to the other incumbent alternative - one could conclude that attraction effect is present. This is suitable for experimental setups where researcher has control over menus and can observe choices in both cases (i.e., in case of an original two-item menu, as well as after adding the third item). However, given that the aim is to generalize context effect measures for application to a wider range of situations, and most importantly to observational data, it is necessary to take a more fine-grained view and quantify the context in which each of the alternatives is embedded. Quantifying the choice context for each alternative would create opportunity to study the effect of the context on choice probabilities through inference across (very) different choice sets. Such an approach would be general enough to consider not only addition of a new alternative to the menu, but also any alteration of attributes for any of the items in the menu. For example, increasing price of an alternative could decrease the probability of its choice. This would have a direct effect on choice probabilities of other alternatives. However, the same price increase could also change the choice context and have additional knock-on effect on choice probabilities of (at least some) alternatives.
